\sysfull

### 2018-04-13 paper/intro.tex
new intro figure
change the intro figure

\begin{wrapfigure}{t!}{0.5\textwidth}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/coalescing-is}
    \caption{\textbf{An execution of three
statically-defined tasks without (top) and with (bottom) dynamic
coalescing.} Task coalescing at runtime reduces time and energy overhead in
task-based intermittent programming models by performing fewer commits and
buffering updates to non-volatile (NV) variables in volatile (V) memory.}
    \label{fig:coalesce}
\end{wrapfigure}

>>>>

\begin{wrapfigure}{t!}{0.5\textwidth}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/Coala_Intro_Figure.pdf}
    \caption{ %\textbf{An execution of three statically-defined tasks without (top) and with (bottom) dynamiccoalescing.}
        Task coalescing at runtime reduces time and energy overhead in
task-based intermittent programming models by performing fewer commits and
buffering updates to non-volatile (NV) variables in volatile (V) memory.}
    \label{fig:coalesce}
\end{wrapfigure}
